\textsc{Does Copyright Affect Reuse?\\ Evidence from Wikipedia and the Google Books Digitization Project}

### 2016-09-20 writing/paper.tex
for final editing and shortening

In order to construct the workhorse sample for the main specification (referred to throughout as Sample A), I followed a five-step process. First, I searched the entire Wikipedia repository for pages that contained mentions of the word \texttt{baseball digest} and variants thereof.  Second, for pages that contained references to Baseball Digest, I accessed and downloaded every past version of the page between 2004 and 2012 as it appeared on December 1 of that year.\footnote{I chose December 1 because this is a few days before the digitization event happened on December 9, 2008.} Third, having collected multiple snapshots of thousands of pages, I wrote python scripts to detect citations to Baseball Digest magazine on each of the individual snapshots. I searched for these citations using pattern matching techniques for a variety of different citation formats because Wikipedia does not follow a standard way to cite source material. However, I found that Wikipedia editors most commonly use the format \emph{Baseball Digest (1963)}, rather than referring to a specific issue, or article within the magazine.\footnote{Although, citations to specific articles or issues can also be found on Wikipedia, I rely on citations to the publication-year to get the largest possible sample of reuse for Baseball Digest.} Accordingly I harmonized all citations by the publication-year of the magazine that was included in a particular citation for all publication-years between 1944 and 1984.\footnote{I choose these years because they form a window of 20 years before and after the copyright cutoff year of 1964.} At this step, I also noted whether the citation was made to an image was being reused, or whether the citation was in the main text of the article. As a fourth and final step, I manipulated these raw data to build Sample A which tracks total citations on Wikipedia to every publication-year of Baseball Digest with one observation for every calendar-year between 2004 and 2012. For example, for a given publication-year, say 1963, Sample A tracks citations on Wikipedia as of 2004, 2005 and so on, up to 2012. In this way, Sample A allowed me to detect the exact year when new citations to a publication-year were added to Wikipedia and to analyze the impact of the 1964 copyright experiment on citations to Baseball Digest before and after the Google Books digitization event.

@@

Consistent with the descriptive analysis, even after flexibly controlling for differences between units of observation and secular time trends, the estimates suggest that out-of-copyright Baseball Digest issues are cited at a significantly higher rate as compared to in-copyright issues across the different specifications. The estimate in Column(2) from the regression using Sample A, which includes both publication-year and wikipedia-year fixed effects suggests that after the digitization event, Baseball Digest issues published before 1964 received about 5.7 more citations as compared to issues published in or after 1964. Compared to the average citation level of about 4.2, this is an increase of almost 135\%. These estimates are somewhat muted although they remain large and significant in the Log specification in Column (3), which suggests that citations to out-of-copyright issues increase by about 34.7\% after the digitization event. The difference between the Log and OLS estimates is important to note,\footnote{One reason for the lower Log-OLS estimates as compared to the OLS estimates could be due to large number of zeros in the outcome variable making the $Log(Cites_{it}+1)$ variable quite consequential.} and the Log estimates should be preferred for a more conservative estimate of the impact of copyright. I will include both OLS and Log specifications in the remaining analysis.

Sample B provides additional evidence for the negative effect of copyright law on preventing the diffusion of material to Wikipedia.\footnote{While the main outcome variable in this case does not count citations to in-copyright and out-of-copyright issues separately, it is very likely that out-of-copyright player-pages make citations to out-of-copyright issues and vice versa.} Specifically, the estimates from Sample B suggest that after the Google Books digitization event, players who made their debut before 1964 (i.e. out-of-copyright players) are more likely to cite material from Baseball Digest as compared to in-copyright players. The OLS estimate from Sample B, Column (2) suggests about 0.2 additional citations as compared to an average of 0.12, an increase of about 160\%. Similarly, the estimates from the log specification are also positive and significant, but are considerably smaller, suggesting an increase in citations of about 7.5\%. This analysis reveals two findings: first, citations to out-of-copyright issues increased significantly after the digitization project and this impact was mostly concentrated among players who made their debut before 1964, i.e. players who were most likely to be affected by the 1964 copyright experiment.

@@

The basic intuition of the descriptive analysis can also be tested in a regression framework. I, therefore, estimate difference-in-difference specifications similar to the baseline specification used for Table \ref{tab:maindd}. The main outcome variables are citations to images and text, rather than the total number of citations. The estimates from this analysis are presented in Table \ref{tab:imgdd}. The estimates indicate that the 1964 copyright cutoff has a more significant impact on the reuse of images rather than text. For example, the second set of estimates for images, which includes both publication-year fixed effects and wikipedia-year fixed effects, suggests that on average out-of-copyright publication-years experience about 5.4 more image citations as compared to in-copyright publication-years. However, the analogous estimate for text citations indicates only a small and statistically insignificant difference in citations between in-copyright and out-of-copyright publication-years. This conclusion is justified even when Log-OLS models are considered. Image citations experience about a 117\% increase while the corresponding increase for text citations is statistically indistinguishable from zero.

@@

Figure \ref{fig:quality} plots these coefficients separately for each quality percentile.\footnote{I plot the coefficient on $out-of-copy \times post_t$ for quality=$1$ and add this estimate to coefficients for other quality levels to compute marginal effects.} Panel (1) validates the hypothesis that the impact of copyright on the reuse of images is larger for the players of lower quality than for players of higher quality. The estimate on the $\hat{\beta}_{n=3}$ coefficient is 0.71 and $\hat{\beta}_{n=4}$ is 0.47, although the second of these two estimates is marginally insignificant. In contrast, the coefficients on $\hat{\beta}_{n=1}$ and $\hat{\beta}_{n=2}$ are both statistically indistinguishable and close to zero. Panel (2), which estimates the impact of copyright on traffic to affected pages, also shows a similar pattern, indicating that the impact on copyright on increasing traffic is also most relevant for players in the lower tier of player quality. This analysis suggests that an important channel through which the digitization of \emph{Baseball Digest} proved useful to Wikipedia was through the unlocking of unique material about \emph{famous-but-not-superstar} players on Wikipedia.

>>>>

In order to construct the workhorse sample for the main specification (referred to throughout as Sample A), I followed a five-step process. First, I searched the entire Wikipedia repository for pages that contained mentions of the word \texttt{baseball digest} and variants thereof.  Second, for pages that contained references to Baseball Digest, I accessed and downloaded every past version of the page between 2004 and 2012 as it appeared on December 1 of that year.\footnote{I chose December 1 because this is a few days before the digitization event happened on December 9, 2008.} Third, having collected multiple snapshots of thousands of pages, I wrote python scripts to detect citations to Baseball Digest magazine on each of the individual snapshots. I searched for these citations using pattern matching techniques for a variety of different citation formats because Wikipedia does not follow a standard way to cite source material. However, I found that Wikipedia editors most commonly use the format \emph{Baseball Digest (1963)}, rather than referring to a specific issue, or article within the magazine.\footnote{Although, citations to specific articles or issues can also be found on Wikipedia, I rely on citations to the publication-year to get the largest possible sample of reuse for Baseball Digest.} Accordingly I harmonized all citations by the publication-year of the magazine that was included in a particular citation for all publication-years between 1944 and 1984.\footnote{I choose these years because they form a window of 20 years before and after the copyright cutoff year of 1964. In theory it would be possible to perform the analysis in this paper with data extending beyond 1984.} At this step, I also noted whether the citation was made to an image was being reused, or whether the citation was in the main text of the article. As a fourth and final step, I manipulated these raw data to build Sample A which tracks total citations on Wikipedia to every publication-year of Baseball Digest with one observation for every calendar-year between 2004 and 2012. For example, for a given publication-year, say 1963, Sample A tracks citations on Wikipedia as of 2004, 2005 and so on, up to 2012. In this way, Sample A allowed me to detect the exact year when new citations to a publication-year were added to Wikipedia and to analyze the impact of the 1964 copyright experiment on citations to Baseball Digest before and after the Google Books digitization event.

@@

Consistent with the descriptive analysis, even after flexibly controlling for differences between units of observation and secular time trends, the estimates suggest that out-of-copyright Baseball Digest issues are cited at a significantly higher rate as compared to in-copyright issues across the different specifications. The estimate in Column(2) from the regression using Sample A, which includes both publication-year and wikipedia-year fixed effects suggests that after the digitization event, Baseball Digest issues published before 1964 received about 5.6 more citations as compared to issues published in or after 1964. Compared to the average citation level of about 4.2, this is an increase of almost 135\%. These estimates are somewhat muted although they remain large and significant in the Log specification in Column (3), which suggests that citations to out-of-copyright issues increase by about 31.6\% after the digitization event. The difference between the Log and OLS estimates is important to note,\footnote{One reason for the lower Log-OLS estimates as compared to the OLS estimates could be due to large number of zeros in the outcome variable making the $Log(Cites_{it}+1)$ variable quite consequential.} and the Log estimates should be preferred for a more conservative estimate of the impact of copyright. I will include both OLS and Log specifications in the remaining analysis.

Sample B provides additional evidence for the negative effect of copyright law on preventing the diffusion of material to Wikipedia.\footnote{While the main outcome variable in this case does not count citations to in-copyright and out-of-copyright issues separately, it is very likely that out-of-copyright player-pages make citations to out-of-copyright issues and vice versa.} In addition the player-page and year fixed effects, these estimates also include fixed effects for page-age, i.e. the number of years since the page was created in the focal year. This additional fixed effect helps control for the concern that more prolific players might have been created earlier, and therefore have had more time to accumulate citations. After adding this additional control, the estimates from Sample B suggest that after the Google Books digitization event, players who made their debut before 1964 (i.e. out-of-copyright players) are more likely to cite material from Baseball Digest as compared to in-copyright players. The OLS estimate from Sample B, Column (2) suggests about 0.2 additional citations as compared to an average of 0.12, an increase of about 160\%. Similarly, the estimates from the log specification are also positive and significant, but are considerably smaller, suggesting an increase in citations of about 6.9\%. This analysis reveals two findings: first, citations to out-of-copyright issues increased significantly after the digitization project and this impact was mostly concentrated among players who made their debut before 1964, i.e. players who were most likely to be affected by the 1964 copyright experiment.

@@

The basic intuition of the descriptive analysis can also be tested in a regression framework. I, therefore, estimate difference-in-difference specifications similar to the baseline specification used for Table \ref{tab:maindd}. The main outcome variables are citations to images and text, rather than the total number of citations. The estimates from this analysis are presented in Table \ref{tab:imgdd}. The estimates indicate that the 1964 copyright cutoff has a more significant impact on the reuse of images rather than text. For example, the second set of estimates for images, which includes both publication-year fixed effects and wikipedia-year fixed effects, suggests that on average out-of-copyright publication-years experience about 5.4 more image citations as compared to in-copyright publication-years. However, the analogous estimate for text citations indicates only a small and statistically insignificant difference in citations between in-copyright and out-of-copyright publication-years. This conclusion is justified even when Log-OLS models are considered. Image citations experience about a 117\% increase while the corresponding increase for text citations is statistically indistinguishable from zero.\footnote{I also repeat this analysis using Sample B in Appendix Table \ref{tab:imgdd_sampleb}. I find positive and large estimates of the impact of out-of-copyright status on reuse for images, while for text, the estimates are positive in OLS models and negative in LOG models, and their magnitude is economically insignificant. See notes in Table \ref{tab:imgdd_sampleb} for more discussion.}

@@

Regression estimates from the specification listed above are presented in Appendix Table \ref{tab:reg_chart_qual}. However, to interpret the results I focus on Figure \ref{fig:quality} which plots these coefficients separately for each quality percentile.\footnote{More accurately, I plot the coefficient on $out-of-copy \times post_t$ for quality=$1$ and add this estimate to coefficients for other quality levels to compute marginal effects.} Panel (1) validates the hypothesis that the impact of copyright on the reuse of images is larger for the players of lower quality than for players of higher quality. The estimate on the $\hat{\beta}_{n=3}$ coefficient is 0.71 and $\hat{\beta}_{n=4}$ is 0.47, although the second of these two estimates is marginally insignificant. In contrast, the coefficients on $\hat{\beta}_{n=1}$ and $\hat{\beta}_{n=2}$ are both statistically indistinguishable and close to zero. Panel (2), which estimates the impact of copyright on traffic to affected pages, also shows a similar pattern, indicating that the impact on copyright on increasing traffic is also most relevant for players in the lower tier of player quality. In order to provide further robustness for these findings, I also replicate this analysis using an alternate measure of player quality by ranking players by their total experience in baseball (better players typically have longer careers), in Appendix Figure \ref{fig:quality_alternate}. This analysis provides further support to the findings from Figure \ref{fig:quality}, however, it seems like the traffic results are supported only for players in the bottom quartile of the quality distribution. Finally, it is important to state that the estimates suggest limited power to establish conclusively that middle-tier players effects are statistically different than effects for lower tier players. More specifically, Table \ref{tab:reg_chart_qual} suggests that these differences are likely to be more robust for the results on page traffic as compared to image reuse.  Despite this caveat, this analysis presented suggests that an important channel through which the digitization of \emph{Baseball Digest} proved useful to Wikipedia was through the unlocking of unique material about \emph{famous-but-not-superstar} players on Wikipedia.

### 2016-09-20 writing/tables.tex
for final editing and shortening

\emph{Note:} This regression estimates the impact of the 1964 copyright exception on affecting the reuse of images and text from Baseball Digest before and after digitization in a differences-in-differences framework. The estimates presented use data from Sample B. \emph{post} refers to all Wikipedia-years after 2008, and \emph{out-of-copy} refers to $publication-year < 1964$. See text for specification, detailed data and variable descriptions.
\end{quote}
\label{tab:imgdd_sampleb}
\end{table}
\end{center}

>>>>

\emph{Note:} This regression estimates the impact of the 1964 copyright exception on affecting the reuse of images and text from Baseball Digest before and after digitization in a differences-in-differences framework. The estimates presented use data from Sample B. \emph{post} refers to all Wikipedia-years after 2008, and \emph{out-of-copy} refers to $publication-year < 1964$. See text for specification, detailed data and variable descriptions. The estimates for images are large and significant relative to the mean. However, the estimates for text are less clear -- being positive in OLS models and negative in LOG models. The magnitude of the estimates for Text reuse are also smaller for OLS estimates as compared the magnitude of estimates for Image reuse. I interpret this evidence as supporting the broad conclusion that out-of-copyright status is more beneficial for image reuse, as compared to text reuse. 
\end{quote}
\label{tab:imgdd_sampleb}
\end{table}
\end{center}
